
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

set.seed(444) #Set up random seed for reproducibility

options(scipen = 999) #Turn off scientific expressions

library(tidyverse)
library(qdapTools)
library(Rmisc)

library(lme4)
library(lmerTest)
library(buildmer)

library(phia)

library(r2glmm)
library(effsize)
library(performance)

rm(list=ls()) #Clear environment

load("Exp3.RData")
```

#F1, Baseline, Word, S2

```{r}
DATA <- read.csv("//wcs-cifs/wc/smng/experiments/simonMultisyllable/acousticdata/R_Zyy/Manuscript/F1_Exp3_S2.csv")

var1 <- length(unique(DATA$Word)) * 10

DATA$Chunk <- ceiling(DATA$Trial/var1)

DATA <- DATA[which(DATA$Phase == "Baseline"), ]

DATA <- DATA[which(DATA$Chunk == max(DATA$Chunk)), ]

DATA <- DATA[which(DATA$Shift != "Unshifted"), ]
```

```{r}
f0 <- meanF1_mel ~ Word + 
  (Word | Speaker)

m.order <- buildmer(f0,
                    data = DATA,
                    buildmerControl=buildmerControl(direction = "order",
                                                    crit = "BIC", 
                                                    args=list(control=lmerControl(optimizer='bobyqa'))))

(f1 <- formula(m.order@model))

m.backward <- buildmer(f1,
                       data = DATA,
                       buildmerControl=list(direction = "backward",
                                            crit = "BIC", 
                                            args=list(control=lmerControl(optimizer='bobyqa'))))

summary(m.backward)

(f2 <- formula(m.backward@model))
```

Fixed effects:
             Estimate Std. Error t value            Pr(>|t|)    
(Intercept)   589.393     13.352  44.143 <0.0000000000000002 ***
Wordpedigree    4.145      4.889   0.848               0.397    


#F1, Baseline, Direction, S2

```{r}
f0 <- meanF1_mel ~ Shift + 
  (Direction | Speaker) + 
  (Direction | Word)

m.order <- buildmer(f0,
                    data = DATA,
                    buildmerControl=buildmerControl(direction = "order",
                                                    crit = "BIC", 
                                                    args=list(control=lmerControl(optimizer='bobyqa'))))

(f1 <- formula(m.order@model))

m.backward <- buildmer(f1,
                       data = DATA,
                       buildmerControl=list(direction = "backward",
                                            crit = "BIC", 
                                            args=list(control=lmerControl(optimizer='bobyqa'))))

summary(m.backward)

(f2 <- formula(m.backward@model))
```

#F2, Baseline, Word, S2
```{r}
DATA <- read.csv("//wcs-cifs/wc/smng/experiments/simonMultisyllable/acousticdata/R_Zyy/Manuscript/F2_Exp3_S2.csv")

var1 <- length(unique(DATA$Word)) * 10

DATA$Chunk <- ceiling(DATA$Trial/var1)

DATA <- DATA[which(DATA$Phase == "Baseline"), ]

DATA <- DATA[which(DATA$Chunk == max(DATA$Chunk)), ]

DATA <- DATA[which(DATA$Shift != "Unshifted"), ]

```

```{r}
f0 <- meanF2_mel ~ Word + 
  (Word | Speaker)

m.order <- buildmer(f0,
                    data = DATA,
                    buildmerControl=buildmerControl(direction = "order",
                                                    crit = "BIC", 
                                                    args=list(control=lmerControl(optimizer='bobyqa'))))

(f1 <- formula(m.order@model))

m.backward <- buildmer(f1,
                       data = DATA,
                       buildmerControl=list(direction = "backward",
                                            crit = "BIC", 
                                            args=list(control=lmerControl(optimizer='bobyqa'))))

summary(m.backward)

(f2 <- formula(m.backward@model))

```

Fixed effects:
             Estimate Std. Error t value             Pr(>|t|)    
(Intercept)  1538.413     12.049  127.69 < 0.0000000000000002 ***
Wordpedigree  -17.819      6.387   -2.79              0.00527 ** 

#F2, Baseline, Shift

```{r}
f0 <- meanF2_mel ~ Shift + 
  (Shift | Speaker) + 
  (Shift | Word)

m.order <- buildmer(f0,
                    data = DATA,
                    buildmerControl=buildmerControl(direction = "order",
                                                    crit = "BIC", 
                                                    args=list(control=lmerControl(optimizer='bobyqa'))))

(f1 <- formula(m.order@model))

m.backward <- buildmer(f1,
                       data = DATA,
                       buildmerControl=list(direction = "backward",
                                            crit = "BIC", 
                                            args=list(control=lmerControl(optimizer='bobyqa'))))

summary(m.backward)

(f2 <- formula(m.backward@model))
```

Fixed effects:
             Estimate Std. Error t value            Pr(>|t|)    
(Intercept)  1530.016     12.642 121.024 <0.0000000000000002 ***
ShiftUpshift   -1.030      7.579  -0.136               0.892

#F3, Baseline, Word
```{r}
DATA <- read.csv("//wcs-cifs/wc/smng/experiments/simonMultisyllable/acousticdata/R_Zyy/Manuscript/F3_Exp3_S2.csv")

var1 <- length(unique(DATA$Word)) * 10

DATA$Chunk <- ceiling(DATA$Trial/var1)

DATA <- DATA[which(DATA$Phase == "baseline"), ]

DATA <- DATA[which(DATA$Chunk == max(DATA$Chunk)), ]

DATA <- DATA[which(DATA$Shift != "Unshifted"), ]
```

```{r}
f0 <- Median ~ Word + 
  (Word | Speaker)

m.order <- buildmer(f0,
                    data = DATA,
                    buildmerControl=buildmerControl(direction = "order",
                                                    crit = "BIC", 
                                                    args=list(control=lmerControl(optimizer='bobyqa'))))

(f1 <- formula(m.order@model))

m.backward <- buildmer(f1,
                       data = DATA,
                       buildmerControl=list(direction = "backward",
                                            crit = "BIC", 
                                            args=list(control=lmerControl(optimizer='bobyqa'))))

summary(m.backward)

(f2 <- formula(m.backward@model))
```

Fixed effects:
             Estimate Std. Error t value            Pr(>|t|)    
(Intercept)   2516.39      61.21   41.11 <0.0000000000000002 ***
Wordpedigree   -14.40      55.40   -0.26               0.795  

#F3, Baseline, Shift

```{r}
f0 <- Median ~ Shift + 
  (Shift | Speaker) +
  (Shift | Word)

m.order <- buildmer(f0,
                    data = DATA,
                    buildmerControl=buildmerControl(direction = "order",
                                                    crit = "BIC", 
                                                    args=list(control=lmerControl(optimizer='bobyqa'))))

(f1 <- formula(m.order@model))

m.backward <- buildmer(f1,
                       data = DATA,
                       buildmerControl=list(direction = "backward",
                                            crit = "BIC", 
                                            args=list(control=lmerControl(optimizer='bobyqa'))))

summary(m.backward)

(f2 <- formula(m.backward@model))
```

Fixed effects:
             Estimate Std. Error t value            Pr(>|t|)    
(Intercept)   2487.87      54.09  45.993 <0.0000000000000002 ***
ShiftUpshift    42.72      54.62   0.782               0.434  

#Save and clear

```{r}
rm(m.backward)
rm(m.order)

save.image("Exp3.RData")
```

