
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

set.seed(444) #Set up random seed for reproducibility

options(scipen = 999) #Turn off scientific expressions

library(tidyverse)
library(qdapTools)
library(Rmisc)

library(lme4)
library(lmerTest)
library(buildmer)

library(phia)

library(r2glmm)
library(effsize)
library(performance)

rm(list=ls()) #Clear environment

load("Exp3.RData")
```

#F1, Baseline, Word, S2

```{r}
DATA <- read.csv("//wcs-cifs/wc/smng/experiments/simonMultisyllable/acousticdata/R_Zyy/Manuscript/F1_Exp3_S2.csv")

var1 <- length(unique(DATA$Word)) * 10

DATA$Chunk <- ceiling(DATA$Trial/var1)

DATA <- DATA[which(DATA$Phase == "Hold"), ]

DATA <- DATA[which(DATA$Chunk == max(DATA$Chunk)), ]

DATA <- DATA[which(DATA$Shift != "Unshifted"), ]
```

```{r}
f0 <- meanF1_mel ~ Word + 
  (Word | Speaker)

m.order <- buildmer(f0,
                    data = DATA,
                    buildmerControl=buildmerControl(direction = "order",
                                                    crit = "BIC", 
                                                    args=list(control=lmerControl(optimizer='bobyqa'))))

(f1 <- formula(m.order@model))

m.backward <- buildmer(f1,
                       data = DATA,
                       buildmerControl=list(direction = "backward",
                                            crit = "BIC", 
                                            args=list(control=lmerControl(optimizer='bobyqa'))))

summary(m.backward)

(f2 <- formula(m.backward@model))
```

Fixed effects:
             Estimate Std. Error t value            Pr(>|t|)    
(Intercept)   592.762     12.062   49.14 <0.0000000000000002 ***
Wordpedigree    3.732      4.056    0.92               0.358   


#F1, Baseline, Direction, S2

```{r}
f0 <- meanF1_mel ~ Shift + 
  (Direction | Speaker) + 
  (Direction | Word)

m.order <- buildmer(f0,
                    data = DATA,
                    buildmerControl=buildmerControl(direction = "order",
                                                    crit = "BIC", 
                                                    args=list(control=lmerControl(optimizer='bobyqa'))))

(f1 <- formula(m.order@model))

m.backward <- buildmer(f1,
                       data = DATA,
                       buildmerControl=list(direction = "backward",
                                            crit = "BIC", 
                                            args=list(control=lmerControl(optimizer='bobyqa'))))

summary(m.backward)

(f2 <- formula(m.backward@model))
```

Fixed effects:
             Estimate Std. Error t value             Pr(>|t|)    
(Intercept)   600.691     11.661  51.511 < 0.0000000000000002 ***
ShiftUpshift  -12.126      2.327  -5.211          0.000000187 ***


#F2, Baseline, Word, S2
```{r}
DATA <- read.csv("//wcs-cifs/wc/smng/experiments/simonMultisyllable/acousticdata/R_Zyy/Manuscript/F2_Exp3_S2.csv")

var1 <- length(unique(DATA$Word)) * 10

DATA$Chunk <- ceiling(DATA$Trial/var1)

DATA <- DATA[which(DATA$Phase == "Hold"), ]

DATA <- DATA[which(DATA$Chunk == max(DATA$Chunk)), ]

DATA <- DATA[which(DATA$Shift != "Unshifted"), ]

```

```{r}
f0 <- meanF2_mel ~ Word + 
  (Word | Speaker)

m.order <- buildmer(f0,
                    data = DATA,
                    buildmerControl=buildmerControl(direction = "order",
                                                    crit = "BIC", 
                                                    args=list(control=lmerControl(optimizer='bobyqa'))))

(f1 <- formula(m.order@model))

m.backward <- buildmer(f1,
                       data = DATA,
                       buildmerControl=list(direction = "backward",
                                            crit = "BIC", 
                                            args=list(control=lmerControl(optimizer='bobyqa'))))

summary(m.backward)

(f2 <- formula(m.backward@model))

```

Fixed effects:
             Estimate Std. Error t value            Pr(>|t|)    
(Intercept)  1536.607     13.899 110.554 <0.0000000000000002 ***
Wordpedigree  -10.099      5.433  -1.859               0.063 .  

#F2, Baseline, Shift

```{r}
f0 <- meanF2_mel ~ Shift + 
  (Shift | Speaker) + 
  (Shift | Word)

m.order <- buildmer(f0,
                    data = DATA,
                    buildmerControl=buildmerControl(direction = "order",
                                                    crit = "BIC", 
                                                    args=list(control=lmerControl(optimizer='bobyqa'))))

(f1 <- formula(m.order@model))

m.backward <- buildmer(f1,
                       data = DATA,
                       buildmerControl=list(direction = "backward",
                                            crit = "BIC", 
                                            args=list(control=lmerControl(optimizer='bobyqa'))))

summary(m.backward)

(f2 <- formula(m.backward@model))
```

Fixed effects:
             Estimate Std. Error t value            Pr(>|t|)    
(Intercept)  1526.356     14.352 106.355 <0.0000000000000002 ***
ShiftUpshift   10.404      5.402   1.926              0.0541 .  

#F3, Baseline, Word
```{r}
DATA <- read.csv("//wcs-cifs/wc/smng/experiments/simonMultisyllable/acousticdata/R_Zyy/Manuscript/F3_Exp3_S2.csv")

var1 <- length(unique(DATA$Word)) * 10

DATA$Chunk <- ceiling(DATA$Trial/var1)

DATA <- DATA[which(DATA$Phase == "hold"), ]

DATA <- DATA[which(DATA$Chunk == max(DATA$Chunk)), ]

DATA <- DATA[which(DATA$Shift != "Unshifted"), ]
```

```{r}
f0 <- Median ~ Word + 
  (Word | Speaker)

m.order <- buildmer(f0,
                    data = DATA,
                    buildmerControl=buildmerControl(direction = "order",
                                                    crit = "BIC", 
                                                    args=list(control=lmerControl(optimizer='bobyqa'))))

(f1 <- formula(m.order@model))

m.backward <- buildmer(f1,
                       data = DATA,
                       buildmerControl=list(direction = "backward",
                                            crit = "BIC", 
                                            args=list(control=lmerControl(optimizer='bobyqa'))))

summary(m.backward)

(f2 <- formula(m.backward@model))
```

Fixed effects:
             Estimate Std. Error t value            Pr(>|t|)    
(Intercept)   2518.00      60.73  41.465 <0.0000000000000002 ***
Wordpedigree   -67.52      42.85  -1.576               0.115    

#F3, Baseline, Shift

```{r}
f0 <- Median ~ Shift + 
  (Shift | Speaker) +
  (Shift | Word)

m.order <- buildmer(f0,
                    data = DATA,
                    buildmerControl=buildmerControl(direction = "order",
                                                    crit = "BIC", 
                                                    args=list(control=lmerControl(optimizer='bobyqa'))))

(f1 <- formula(m.order@model))

m.backward <- buildmer(f1,
                       data = DATA,
                       buildmerControl=list(direction = "backward",
                                            crit = "BIC", 
                                            args=list(control=lmerControl(optimizer='bobyqa'))))

summary(m.backward)

(f2 <- formula(m.backward@model))
```

Fixed effects:
             Estimate Std. Error t value            Pr(>|t|)    
(Intercept)   2478.07      62.74   39.49 <0.0000000000000002 ***
ShiftUpshift    12.27      45.48    0.27               0.787    

#F1 change in the Hold

```{r}
DATA <- read.csv("//wcs-cifs/wc/smng/experiments/simonMultisyllable/acousticdata/R_Zyy/Manuscript/F1_Exp3_S2.csv")

var1 <- length(unique(DATA$Word)) * 10

DATA$Chunk <- ceiling(DATA$Trial/var1)

#Normalization

data <- DATA[which(DATA$Phase %in% c("Baseline")), ]
data <- data[which(data$Chunk == max(data$Chunk)), ]

temp1 <- aggregate(data$meanF1_mel, 
                   list(data$Shift, data$Speaker), 
                   FUN = mean) 

colnames(temp1) <- c("Direction", "Speaker", "F1_Baseline")

DATA$Tracer <- paste(DATA$Shift, DATA$Speaker, sep = "_")
temp1$Tracer <- paste(temp1$Direction, temp1$Speaker, sep = "_")

DATA$F1_Baseline <- lookup(terms = DATA$Tracer,
                         key.match = temp1$Tracer,
                         key.reassign = temp1$F1_Baseline)

DATA$F1_Change <- DATA$meanF1_mel - DATA$F1_Baseline
```

```{r}
#Modeling

table(DATA$Chunk, DATA$Phase)

data <- DATA[which(DATA$Chunk %in% c(12, 13)), ]
data <- data[which(data$Shift != "Unshifted"), ]

f0 <- F1_Change ~ Shift * Phase + 
  (Shift * Phase | Speaker) + 
  (Shift * Phase | Word)

m.order <- buildmer(f0,
                    data = data,
                    buildmerControl=buildmerControl(direction = "order",
                                                    crit = "BIC", 
                                                    args=list(control=lmerControl(optimizer='bobyqa'))))

(f1 <- formula(m.order@model))

m.backward <- buildmer(f1,
                       data = data,
                       buildmerControl=list(direction = "backward",
                                            crit = "BIC", 
                                            args=list(control=lmerControl(optimizer='bobyqa'))))

summary(m.backward)

(f2 <- formula(m.backward@model))
```

```{r}
m3_S2 <- lmer(f2,
           data = data,
           control = lmerControl(optimizer = "bobyqa",
                                 optCtrl = list(maxfun = 2e5)),
           REML = TRUE)

car::Anova(m3_S2, type = 3)

formula(m3_S2)

r2beta(m3_S2, partial = TRUE, 
       method = "nsj")

testInteractions(m3_S2,
                 pairwise = "Shift",
                 fixed = "Phase")

testInteractions(m3_S2,
                 fixed = "Shift")

```

```{r}
#Summary

aggregate(data$F1_Change,
          list(data$Shift, data$Phase), 
                   FUN = mean) 

aggregate(data$F1_Change,
          list(data$Shift, data$Phase), 
                   FUN = plotrix::std.error) 


aggregate(data$F1_Change,
          list(data$Shift), 
                   FUN = plotrix::std.error) 

#Cohen's d, Direction

temp1 <- data[which(data$Shift == "Downshift"), "F1_Change"]
temp2 <- data[which(data$Shift == "Upshift"), "F1_Change"]

cohen.d(temp1, temp2)


temp1 <- data[which(data$Shift == "Downshift" & data$Phase == "Hold"), "F1_Change"]
temp2 <- data[which(data$Shift == "Upshift" & data$Phase == "Hold"), "F1_Change"]

cohen.d(temp1, temp2)

temp1 <- data[which(data$Shift == "Downshift" & data$Phase == "Washout"), "F1_Change"]
temp2 <- data[which(data$Shift == "Upshift" & data$Phase == "Washout"), "F1_Change"]

cohen.d(temp1, temp2)
```


#Save and clear

```{r}
rm(m.backward)
rm(m.order)

save.image("Exp3.RData")
```

